---
title: "Weight of Fish"
author: "Carly Syms"
date: "Spring 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
AllFish <- read.csv(file = "Fish.csv")
AllFish$Species <- as.factor(AllFish$Species)
levels(AllFish$Species)
```

```{r}
Perch <- subset(AllFish, Species == "Perch")
Perch <- select(Perch, -Species)
Bream <- subset(AllFish, Species == "Bream")
Bream <- select(Bream, -Species)
Smelt <- subset(AllFish, Species == "Smelt")
Smelt <- select(Smelt, -Species)
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
From the plot above we see that the two best regression models are Height and Width. The model of the Height and Width are the adjusted R-squared of about 0.94.
  
## Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```

```{r}
PerchModel <- lm(Weight~Height+Width, data = Perch)
summary.lm(PerchModel)
```

Here we get that the adjusted R-square is 0.94, which is the best model because its R-squared is the highest. The residual satndard error 85.17

# Bream

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
From the plot above we see that the two best regression models are Length1, Height, and Width. The model of the Height and Width are the adjusted R-squared of about 0.94.
  
## Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```

```{r}
BreamModel <- lm(Weight~Height+Length2, data = Bream)
summary.lm(BreamModel)
```

The adjusted R-squared of Height and Length2 is 0.9356. The residual standard error of the two best regression models is 53.1. 

# Smelt

